Technical Report

### 2018-06-19 fully-abstract-comp/technical-report.tex

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A,\gc}{v} \defeq (v,H_A^{\mathrm{std},\square} \; \gc) , v \in \{\spa,\spao\}
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\[
  \stdreg{A,\gc}{\pur} \defeq (\pur,H_A^{\mathrm{std},\square} \; \gc, \lambda \_ \; \_ \ldotp \emptyset)
\]
where $H^{\mathrm{std},\square}_A$ is defined as follows:
\[
  H_A^{\mathrm{std},\square} \; \gc \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : A \fun \World \ldotp \xi(\hat{W}) = \oplus_{\aaddr \in A} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]
\lau{01-11-2017: RESOLVED look into what kind of world separation should happen here.}
%\dominique{7-3-2018: is it necessary to have $n-1$ above? there is already a quantification over $n'<n$ in the memory satisfaction relation.} \lau{04-04-2018: The n'<n was removed from memory satisfaction.}

@@

\begin{lemma}
  If
  \begin{itemize}
  \item $\npair{(\reg_S,\_)} \in \lrr(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$for all $r \not\in \{\pcreg\}$
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove the three results separately:
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ for all $r \not\in \{\pcreg\}$:

    We have that $W = \bigoplus_{r \in \RegName \setminus \{\pcreg\}} S(r)$ and $\npair{(\reg_S(r),\reg_T(r))} \in \lrv(S(r))$ for all $r \not\in \{\pcreg\}$.

    TODO

  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint:

>>>>

\subsection{Standard regions}
\label{sec:standard-regions}
Standard region:
\[
  \stdreg{A,\gc}{v} \defeq (v,H_A^{\mathrm{std},\square} \; \gc) , v \in \{\spa,\spao\}
\]
for readability, we use $\spao$ short for $\spatialo$, $\spa$ short for $\spatial$, and $\pur$ as short for $\pure$.
\[
  \stdreg{A,\gc}{\pur} \defeq (\pur,H_A^{\mathrm{std},\square} \; \gc, \lambda \_ \; \_ \ldotp \emptyset)
\]
where $H^{\mathrm{std},\square}_A$ is defined as follows:
\[
  H_A^{\mathrm{std},\square} \; \gc \; \hat{W} \defeq \left\{ \npair{\ms_S,\ms_T} \middle|
    \begin{array}{l}
      \dom(\ms_S) = \dom(\ms_T) = A \wedge \\
      \exists S : A \fun \World \ldotp \xi(\hat{W}) = \oplus_{\aaddr \in A} S(\aaddr) \wedge\\
      \quad \forall \aaddr \in A \ldotp \npair{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(S(\aaddr))
    \end{array}
  \right\}
\]
\lau{01-11-2017: RESOLVED look into what kind of world separation should happen here.}

@@

\begin{lemma}
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(\reg_S,\_)} \in \lrr(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  \begin{itemize}
  \item $\reg_S(r)$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$ for all $r \not\in \{\pcreg\}$
  \item $\ms_S$, $\ms_\stk$ and $\stk$ are all disjoint
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove the three results separately:
  \begin{itemize}
  \item $\reg_S(r)$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$ for all $r \not\in \{\pcreg\}$:

    We have that $W_w = \bigoplus_{r \in \RegName \setminus \{\pcreg\}} S(r)$ and $\npair{(\reg_S(r),\reg_T(r))} \in \lrv(S(r))$ for all $r \not\in \{\pcreg\}$.

    For all $r \neq \pcreg$, we have that $\purePart{S(r)} \oplus \purePart{W_M}$ is defined by Lemmas~\ref{lem:purePart-oplus} and~\ref{lem:oplus-assoc-comm}.

    The result then follows directly from Lemma~\ref{lem:untrusted-source-values-are-reasonable}.

  \item $\ms_S$, $\ms_\stk$ and $\stk$ are all disjoint:
